Evaluating the Performance and Energy Efficiency of the \textsc{COSMO-ART} model system

### 2014-04-25 trunk/paper_enahpc14/Sec4:Experimental-results.tex
Manuel's changes

\subsection{Time-power-energy analysis of \textsc{Cosmo-art}}
\label{subsec:4.2}

\begin{figure}[htbf]
  \begin{center}
    \includegraphics[width=0.48\textwidth]{Figs/NRJ_benchmark_Monch.eps}
    \caption{\textsc{Monch}: Isola E1 Rack 2 Total Power}
    \label{fig:1}
  \end{center}
\end{figure}

\begin{figure}[htbf]
  \begin{center}
    \includegraphics[width=0.48\textwidth]{Figs/NRJ_benchmark_Pilatus.eps}
    \caption{\textsc{Pilatus}: Isola HD Total Power}
    \label{fig:2}
  \end{center}
\end{figure}

@@

\subsection{Power-performance tracing of \textsc{Cosmo-art}}
\label{subsec:4.3}

@@

\begin{figure*}[htbf]
  \centering
  \scriptsize
  MPI polling mode\\
  \scalebox{0.5}{\input{Figs/11_12_blq0_figure.pstex_t}}\\
  MPI blocking mode\\
  \scalebox{0.5}{\input{Figs/11_12_blq1_figure.pstex_t}}\\
  MPI polling mode\\
  \scalebox{0.5}{\input{Figs/23_24_blq0_figure.pstex_t}}\\
  MPI blocking mode\\
  \scalebox{0.5}{\input{Figs/23_24_blq1_figure.pstex_t}}\\
  \caption{1 hour simulation (23h-24h) trace using the MPI blocking
    mode on \textsc{Tintorrum}.}
  \label{fig:11}
\end{figure*}

>>>>

\subsection{Time-power-energy analysis of \cosmoart}
\label{subsec:4.2}

\begin{figure}[htbf]
  \begin{center}
    \includegraphics[width=0.48\textwidth]{Figs/NRJ_benchmark_Monch.eps}
    \caption{\textsc{Monch}: Isola E1 Rack 2 Total Power.}
    \label{fig:1}
  \end{center}
\end{figure}

\begin{figure}[htbf]
  \begin{center}
    \includegraphics[width=0.48\textwidth]{Figs/NRJ_benchmark_Pilatus.eps}
    \caption{\textsc{Pilatus}: Isola HD Total Power.}
    \label{fig:2}
  \end{center}
\end{figure}

@@

\subsection{Power-performance tracing of \cosmoart}
\label{subsec:4.3}

A full tracing experiment is conducted on \tinto in order to capture an overall power
profile at a much finer resolution. First we run \cosmoart for a full-day simulation
and analyze the power consumption. Second we correlate performance with
power traces of two 1-hor time frames during the day: midday (from 11h-12h) and
midnight (23-24h).

For all the experiments we also analyze the contribution of the MPI library to the energy consumption and how the use of the blocking versus polling message-passing policies can potentially render energy savings. Specifically, the OpenMPI 1.6.5 library installed in \tinto, features two operation modes, blocking and modes, which can be selected before \cosmoart is launched. In the polling configuration (the detault mode) ``MPI'' continually polls
the netwrok interface to check for the completion of an event (e.g. send or receive).
This usually yields low latency but high CPU utilization. Thus, can one expcet that this mode attanins the best performance, possibley at the cost a higher energy usage. In the blocking
mode, the CPU is yield to other processes/threads if there are no incoming messages.

@@

\begin{figure*}[htbf]
  \centering
  \scriptsize
  Simulation of 1 hour during midday (from 11h to 12h) leveraging the polling MPI policy\\
  \scalebox{0.5}{\input{Figs/11_12_blq0_figure.pstex_t}}\\
  Simulation of 1 hour during midday (from 11h to 12h) leveraging the blocking MPI policy\\
  \scalebox{0.5}{\input{Figs/11_12_blq1_figure.pstex_t}}\\
  Simulation of 1 hour during midnight (from 23h to 24h) leveraging the polling MPI policy\\
  \scalebox{0.5}{\input{Figs/23_24_blq0_figure.pstex_t}}\\
  Simulation of 1 hour during midnight (from 23h to 24h) leveraging the blocking MPI policy\\
  \scalebox{0.5}{\input{Figs/23_24_blq1_figure.pstex_t}}\\
  \begin{tabular}{rlp{-0.2cm}rlp{-0.2cm}rlp{-0.2cm}rlp{-0.2cm}rlp{-0.2cm}rl}
& &  & &  & &  & &  \\[-0.15cm]
Computation     & \multicolumn{1}{>{\columncolor[RGB]{  0,  , 255}}p{0.4cm}}{}  & & 
Waiting a msg.  & \multicolumn{1}{>{\columncolor[RGB]{255,  0  ,0}}p{0.4cm}}{}  & & 
Block. send     & \multicolumn{1}{>{\columncolor[RGB]{255,  0,174}}p{0.4cm}}{}  & & 
Synchronization & \multicolumn{1}{>{\columncolor[RGB]{179,  0,  0}}p{0.4cm}}{}  & & 
Wait/Wait all   & \multicolumn{1}{>{\columncolor[RGB]{235,  0,  0}}p{0.4cm}}{}  \\
& &  & &  & &  & &  \\[-0.15cm]
Immediate recv. & \multicolumn{1}{>{\columncolor[RGB]{100,100,177}}p{0.4cm}}{}  & &
I/O             & \multicolumn{1}{>{\columncolor[RGB]{172,174, 41}}p{0.4cm}}{}  & &
Group comm.     & \multicolumn{1}{>{\columncolor[RGB]{255,144, 26}}p{0.4cm}}{}  & &
Others          & \multicolumn{1}{>{\columncolor[RGB]{192,224,  0}}p{0.4cm}}{}  & &
Idle            & \multicolumn{1}{>{\columncolor[RGB]{117,195,255}}p{0.4cm}}{}  \\
\end{tabular}
  \caption{Power-perfomance traces during midday and midnight leveraging the polling and blocking MPI policies on \tinto.}
  \label{fig:11}
\end{figure*}
